2-factor-Hull-White\_model\_calibration

### 2020-05-12 week7/Report.tex
Added More Citations

\section{Conclusion}
In this paper, we simulated correlated firm and share price paths. From this, we priced an up-and-out call option at 8.299 with a default-free risk profile, and at 8.281 for the CVA-adjusted price. Considering that the same parameters are used as the first submission, where the Black-Scholes-Merton model was used to arrive at a price of 5.697, we observe that both the default risk, the variable interest rate and local volatility have all added a premium to the option price. These conditions, which are more aligned to observed market conditions, gave a total increase of 45\% over the previously calculated price, with the default risk accounting for only 0.2\% of the difference. These results underline the importance of choosing the correct model and performing accurate calibration in order to calculate instrument prices.

@@

% the second parameter MMMMM should be as long as the longest label you use, in my case Smoller -- if you use % numbers only, use 99
% use \cite{refname} to refer to bibliography item \bibitem{refname}
% LaTeX assigns a number, unless you use \bibitem[Name]{refname} -- in this case
% LaTeX prints Name when you use \cite{refname}
\begin{thebibliography}{MMMMM}
\bibitem{Vas1} Vasicek, O. (1977). An equilibrium characterization of the term structure, Journal of financial economics 5(2): 177-188.
\bibitem{Mamon1} Mamon, R. S. (2004). Three ways to solve for bond prices in the vasicek model, Advances in Decision Sciences 8(1): 1-14.
\bibitem{HW1} Hull, J. and White, A. (2001). The general hull-white model and supercalibration, Financial Analysts Journal pp. 34-43.
\bibitem{CIR1} Cox, J. C., Ingersoll Jr, J. E. and Ross, S. A. (1985). An intertemporal general equilibrium model of asset prices, Econometrica: Journal of the Econometric Society pp. 363-384.
\bibitem{AMST1} Albrecher, H., Mayer, P., Schoutens, W. and Tistaert, J. (2007).
``The Little Heston Trap'', Wilmott (1): 83--92.
\bibitem{Cox1}  Cox, John. "Notes on option pricing I: Constant elasticity of variance diffusions." Unpublished note, Stanford University, Graduate School of Business (1975).
\bibitem{M5} MScFE630 Computational Finance Module 5: Monte Carlo Methods for Risk Management
\bibitem{M6} MScFE630 Computational Finance Module 6: Pricing Interest Rate Options
\bibitem{M7} MScFE630 Computational Finance Module 7: Calibration

>>>>

\section{Conclusion}
In this paper, we simulated correlated firm and share price paths. From this, we priced an up-and-out call option at 8.296 with a default-free risk profile, and at 8.278 for the CVA-adjusted price. Considering that the same parameters are used as the first submission, where the Black-Scholes-Merton model was used to arrive at a price of 5.697, we observe that both the default risk, the variable interest rate and local volatility have all added a premium to the option price. These conditions, which are more aligned to observed market conditions, gave a total increase of 45\% over the previously calculated price, with the default risk accounting for only 0.2 of the difference. These results underline the importance of choosing the correct model and performing accurate calibration in order to calculate instrument prices.

@@

% the second parameter MMMMM should be as long as the longest label you use, in my case Smoller -- if you use % numbers only, use 99
% use \cite{refname} to refer to bibliography item \bibitem{refname}
% LaTeX assigns a number, unless you use \bibitem[Name]{refname} -- in this case
% LaTeX prints Name when you use \cite{refname}
\begin{thebibliography}{MMMMM}
\bibitem{Vas1} Vasicek, O. (1977). An equilibrium characterization of the term structure, Journal of financial economics 5(2): 177-188.
\bibitem{Mamon1} Mamon, R. S. (2004). Three ways to solve for bond prices in the vasicek model, Advances in Decision Sciences 8(1): 1-14.
\bibitem{HW1} Hull, J. and White, A. (2001). The general hull-white model and supercalibration, Financial Analysts Journal pp. 34-43.
\bibitem{CIR1} Cox, J. C., Ingersoll Jr, J. E. and Ross, S. A. (1985). An intertemporal general equilibrium model of asset prices, Econometrica: Journal of the Econometric Society pp. 363-384.
\bibitem{Mer1} Merton, Robert C. "Theory of rational option pricing." The Bell Journal of economics and management science (1973): 141-183.
\bibitem{Cox1}  Cox, John. "Notes on option pricing I: Constant elasticity of variance diffusions." Unpublished note, Stanford University, Graduate School of Business (1975).
\bibitem{RD1} Rich, Don R. "The mathematical foundations of barrier option-pricing theory." Advances in futures and options research 7 (1994).
\bibitem{WK1} Wong, Hoi Ying, and Yue‐Kuen Kwok. "Multi-asset barrier options and occupation time derivatives." Applied Mathematical Finance 10.3 (2003): 245-266.
\bibitem{BS1}Black, Fisher, and Myron Scholes. "The pricing and Corportate Liabilities." Journal of Political Economy 81 (1973).
\bibitem{You1} Yousuf, M. "A fourth-order smoothing scheme for pricing barrier options under stochastic volatility." International Journal of Computer Mathematics 86.6 (2009): 1054-1067.
\bibitem{M5} MScFE630 Computational Finance Module 5: Monte Carlo Methods for Risk Management
\bibitem{M6} MScFE630 Computational Finance Module 6: Pricing Interest Rate Options
\bibitem{M7} MScFE630 Computational Finance Module 7: Calibration
